
%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
    \project
	{Centralised Order Management System}{2021 - Now}
	{\website{https://manager.thinkingfoods.com/}{Thinking Foods}}
	{
	    Centralised Order Management system for ThinkingFoods company in Spain. This system integrate multiple e-commerce websites and provide centralised overview with an analytic platform. Feature rich system with delivery management, order management, email and sms notifications.  
	}
	{Python, React, MySQL, AWS Lambda}
	\\	
	\project
	{Sysco Shop}{2019 - Now}
	{\website{http://shop.sysco.com}{shop.sysco.com} }
	{
	   Sysco Shop is a complete marketplace for Sysco customers. Mainly worked on ordering platform which is
	    responsible of processing millions of orders per a week. Involved in designing backend architecture, development of supporting micro-services, integration between different components, maintaining micro services, databases and other components. Rigorous testing and automated deployment and state of the art infrastructure setup with kubernetes. Proactive service monitoring.  
	}
	{Springboot, Node.js, React, Docker, Kubernetes, AWS, Jenkins, DataDog}
	\\		
	\project
	{Centralized log monitoring system for OrangeHRM}{Sep - Oct’17}
	{\website{https://www.orangehrm.com}{Orange HRM}}
	{
	    A complete log collecting, monitoring and alerting system for more
        than 10 servers.
	}
	{Elasticsearch, Logstash, Kibana, Beats}
	\\
	\project
	{CICD pipelines for OrangeHRM}{Jul - Aug’17}
	{\website{https://www.orangehrm.com}{Orange HRM} \github{orangehrm/orangehrm}}
	{
	    A complete log collecting, monitoring and alerting system for more
        than 10 servers.
	}
	{Docker, Jenkins, Travis, Codeception, Git, Subversion}

\end{projects}